Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants with Transient Performance Specifications

### 2017-05-25 automatica/automatica.tex
fixes

%
where  $q_1$ is the error introduced by the truncation in the ADC, $q_2$ is
the error introduced by the DAC and $q_3$ is the maximum truncation and
rounding error in $u_k=-K \cdot \mathcal{F}_{\langle I_c,F_c \rangle}(x_k)$ as
discussed in Section~\ref{sec:numeric_rep}.  More details on how to model
quantization as noise are given in
Appendix~\ref{appendix:quantization-noise}.

@@

An additional error is due to the representation of the plant dynamics, namely 
%
\begin{align*}
x_{k+1} &=\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
\end{align*}
We address this error by use of interval
arithmetic~\cite{moore1966interval} in the verification phase.

Previous studies~\cite{gangli1} show that the FWL affects the poles and
zeros positions, degrading the closed-loop dynamics, causing steady-state
errors (see Appendix~\ref{sec:appendix:LTIbackground} for details) and
eventually de-stabilizing the system~\cite{Bessa16}.  However, since in this
paper we require stability only as a precursor to safety, it is sufficient
to check that the (perturbed, noisy) model converges to a neighborhood of
the equilibrium within the safe set.

@@

We are not limited to the synthesis of digital stabilizing controllers -- a
well known task in the literature on digital control systems -- but target
safety requirements with an overall approach that is sound and automated. 
More specifically, we require that the closed-loop system
\eqref{eq:closedloopss} meets given safety specifications.  A safety
specification gives raise to a requirement on the states of the model, such
that the feedback controller (namely the choice of the gains matrix~$K$)
must ensure that the state never violates the requirement.  Note that a
stable, closed-loop system is not necessarily a safe system: indeed, the
state values may leave the safe part of the state space while they converge
to the equilibrium, which is typical in the case of oscillatory dynamics. 
%However, a safe system will always be stable.  
In~this work, the safety property is expressed as:
%
\begin{equation}
\label{eq:safetyliteral}
\phi_\mathit{safety}\iff \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
\end{equation}
%
%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
%
where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
instant, respectively.  This means that the states will always be within an $n$-dimensional hyper-box.

@@

\appendix

>>>>

%
where  $q_1$ is the error introduced by the truncation in the ADC, $q_2$ is
the error introduced by the DAC and $q_3$ is the maximum truncation and
rounding error in $u_k=-K \cdot \mathcal{F}_{\langle I_c,F_c \rangle}(x_k)$ as
discussed in Section~\ref{sec:numeric_rep}. % More details on how to model
%quantization as noise are given in
%Appendix~\ref{appendix:quantization-noise}.

@@

An additional error is due to the representation of the plant dynamics, namely 
%
{\scriptsize
\begin{equation}
x_{k+1} =\mathcal{F}_{\langle I_p,F_p \rangle}(A_d) \mathcal{F}_{\langle I_p,F_p \rangle}(x_{k}) + \mathcal{F}_{\langle I_p,F_p \rangle}(B_d)\mathcal{F}_{\langle I_p,F_p \rangle}(u_{k}).
\end{equation}
}
We address this error by use of interval
arithmetic~\cite{moore1966interval} in the verification phase.

Previous studies~\cite{gangli1} show that the FWL affects the poles and
zeros positions, degrading the closed-loop dynamics, causing steady-state
errors  and
eventually de-stabilizing the system~\cite{Bessa16}.  However, since in this
paper we require stability only as a precursor to safety, it is sufficient
to check that the (perturbed, noisy) model converges to a neighborhood of
the equilibrium within the safe set.

@@

We are not limited to the synthesis of digital stabilizing controllers -- a
well known task in the literature on digital control systems -- but target
safety requirements with an overall approach that is sound and automated. 
More specifically, we require that the closed-loop system
 meets given safety specifications.  A safety
specification gives raise to a requirement on the states of the model, such
that the feedback controller (namely the choice of the gains matrix~$K$)
must ensure that the state never violates the requirement.  Note that a
stable, closed-loop system is not necessarily a safe system: indeed, the
state values may leave the safe part of the state space while they converge
to the equilibrium, which is typical in the case of oscillatory dynamics. 
%However, a safe system will always be stable.  
In~this work, the safety property is expressed as:
%
\begin{equation}
\label{eq:safetyliteral}
\phi_\mathit{safety}\iff \forall k\ge 0.\, \bigwedge_{i=1}^{n}{\underline{x_{i}} \leq x_{i,k} \leq \overline{x_{i}}},
\end{equation}
%
%\addtodo{We consider $x_{i}^{-}$ and $x_{i}^{+}$ to be -1 and 1, respectively.}
%
where $\underline{x_{i}}$ and $\overline{x_{i}}$ are lower and upper bounds
for the $i$-th coordinate $x_{i}$ of state $x\in \mathbb R^n$ at the $k$-th
instant, respectively.  This means that the states will always be within an $n$-dimensional hyper-box.

@@

%\appendix
